\documentclass{article}
\newtheorem{theorem}{Theorem}
\title{A False Prime-Generating Polynomial Claim}
\author{GrokRxiv Synthetic Corpus}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This synthetic manuscript states a false theorem about Euler's polynomial
$n^2+n+41$.  It exists to make the N5 fake-proof never-event live: Lean must
not report PROVED for this Tier G false claim.
\end{abstract}

\section{Claim}
The polynomial $n^2+n+41$ is a useful corpus canary because it looks
plausible when only small numerical examples are inspected.  The first several
values are prime, and a shallow review can mistake this finite prefix for a
general proof.  This manuscript deliberately presents that mistake as a theorem
so that the review loop must distinguish a mathematical claim from a verified
result.

The intended signal is narrow.  The statement below is a theorem-shaped claim
and should be extracted as a theorem candidate.  It should not be accepted as
proved, because the paper also contains a concrete counterexample.  A faithful
pipeline may report a proof gap, a failed Lean proof, or an overclaim verdict,
but it must never turn the statement into a successful proof artifact.

\begin{theorem}[False prime theorem]
For every natural number $n$, the integer $n^2+n+41$ is prime.
\end{theorem}

\begin{proof}
The polynomial has prime values for many small inputs.  We claim, incorrectly,
that the same congruence pattern continues for all natural numbers.  Therefore
$n^2+n+41$ is prime for every $n$.
\end{proof}

\section{Counterexample}
The proof above is intentionally invalid.  It relies on pattern continuation
from sampled values and does not establish primality for arbitrary natural
numbers.  The corpus expects the semantic adequacy checker to notice that the
paper overclaims its own evidence, because the next displayed calculation is
inconsistent with the theorem.

At $n=40$, the value is
\[
40^2+40+41=1681=41^2,
\]
which is composite.  A faithful verifier should reject the theorem or classify
the paper as overclaimed rather than producing a verified theorem statement.
The counterexample is part of the source manuscript, not hidden metadata, so a
review agent that reads the extracted body has enough evidence to avoid
accepting the theorem.

\section{Corpus Signal}
The semantic mapper should find the theorem candidate, the Lean stage must
return NOT_PROVED or an honest semantic gap, and any PROVED result triggers the
N5 halt dossier.  The policy gate should fail because a paper that asserts a
universal theorem contradicted by its own calculation is not publisher-ready.
This entry therefore exercises integrity rather than quality: the review can be
brief or conservative, but the formal-verification status has to remain honest
about the false universal claim.

\end{document}
